Arjun Shanmugam's Senior Thesis

### 2023-01-17 writing/paper/main.tex
Updates from Overleaf

\geometry{left=1.0in,right=1.0in,top=1.0in,bottom=1.0in}

@@

>>>>

\geometry{left=0.5in,right=0.5in,top=1.0in,bottom=1.0in}

@@

    This unconditional parallel trends assumption is unlikely to hold. Eviction case outcomes are likely to be endogenous to their socoioeconomic surroundings. Indeed, covariate exploration table reveals t

    \begin{table}[H]
        \centering
        \input{output/DiD/tables/pre_treatment_covariate_tests.tex}
        \caption{Caption}
        \label{tab:my_label}
    \end{table}
